Species turnover reveals hidden effects of decreasing Nitrogen deposition in mountain hay meadows

### 2018-10-23 Manuscript.Rmd
Small changes in Introduction.

DISCUSSION ABOUT TEMPORAL TURNOVER.
- Stimmt mit vielen Studien überein, dass temporal turnover sehr gross ist.
- Unser Vergleich mit Doppelaufnahmen zeigt aber auch, dass man vorsichtig mit der Interpretation sein muss und dass auch standardisierte Monitoringprogramme ein relative hohe Pseudo-Turnover zeigen, die von unterschiedenen zwischen zwei Aufnahmen herrühren.
- Trotzdem finden wir Muster, die kaum auf Methodische Gründe Zurückzuführen sind. Zum Beispiel ist Turnover bei tiefer N Dep am höchsten. Aber warum ist das so?
- Ev auch noch den Anteil der Perennial diskutieren --> Turnover ist erstaunlich hoch.

>>>>

Our results conform to the results of recent reviews on biodiversity change suggesting that local-scale species communities are undergoing biodiversity change but not systematic loss [@Dornelas2014]. However, our comparision with replicated surveys also warn that an important portion of the observed turnover could be caused by pseudo-turnover (i.e. the proportion of species that differed between two surveys that were conducted by two different surveyors during the same year on the same site). Given that the BDM program invested significantly in developing and testing reproducable methods and quality control [@Plattner2004], the pseudo-turnover was still quite high. A potential explanation is that there are usually few days between the replicated surveys and in few cases the situation might have changeed profoundly for example if the meadow was cut. Furthermore, for difficult to identify species one of the botanist may only note the species pair and not identify the plant on the species level.

The BDM programme contains relatively clearly described methods and The BDM therefore invests signifi- cantly in developing and testing appropriate methods.

- Unser Vergleich mit Doppelaufnahmen zeigt aber auch, dass man vorsichtig mit der Interpretation sein muss und dass auch standardisierte Monitoringprogramme ein relative hohe Pseudo-Turnover zeigen, die von unterschiedenen zwischen zwei Aufnahmen herrühren.
- Trotzdem finden wir Muster, die kaum auf Methodische Gründe Zurückzuführen sind. Zum Beispiel ist Turnover bei tiefer N Dep am höchsten. Aber warum ist das so?
- Ev auch noch den Anteil der Perennial diskutieren --> Turnover ist erstaunlich hoch.
